Comparative study of Dask and Spark for neuroimaging pipelines

### 2019-06-10 latex/acl2019.tex
Modified exp1 - # of instances and # of itr

% Histogram
\subsection{Histogram}
For our second experiment we find the frequency of the voxels intensity in BigBrain
and save them as a tuple in a file. In this experiment the end results depends on all
of the input results (see \ref{fig:tg-histo}). This allow us to study the behaviour
of the framework when task are dependent. Also this application require data
shuffling thus inter worker communication. In this application we decided to only
compare Spark against the Dask bag and array API as they are the more realistic for
this use case.

@@

%%% INCREMENTATION %%%
%% Instances
\subsection{Experiment 1: Number of instances}
Figure \ref{fig:inc_node} shows that has the number of node increase the performance
decrease. The reason we think this happen is that the number of workers becomes
larger than the number of tasks to process. Also, as more worker access the nfs
simultaneously this increase the stress put on the system which result in bottleneck,
errors and slow down. On the one hand, Dask seems better when using a single worker.
On the other hand, Spark makespan decrease faster for low level of parallelism.
However Dask quickly catch up at high level of parallelism. This makes us think that
the scheduler in Dask might be better

\begin{figure}[p]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_instances.png}%
    }

@@

%% Iterations
\subsection{Experiment 1: Number of iterations}
In Figure \ref{fig:inc_itr} Dask futures grows faster than the other API. This is due
to the lack of optimization on the real time processing of tasks. The Dask bag with
graph optimization seems to perform worst than other as the number of tasks increase.
This might show that over optimizing task graph results in performance decrease. When
the task load start to grow slightly Dask bag seems to be the best option. This could
be explained as Dask bag is the most optimized Dask's API that we compare. Also Spark
serialization could slow down the execution as the number of task increase thus
reducing its optimization effects

\begin{figure}[p]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_iterations.png}%
    }

@@

%% Sleep time
\subsection{Experiment 1: Sleep delay}
As Figure \ref{fig:inc_sleep} shows, Dask is way faster than Spark for any task
length. We can consider optimising the graph for shorter task but it seams that
normal Dask bag have better optimization policy for longer task. However the results
are surprising since the makespan should increase as the sleep delay increase but we
see the inverse effect.

\begin{figure}[p]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_sleeptime.png}%
    }

@@

\begin{figure}[p]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_splits.png}%
    }

@@

\begin{figure}[p]
    \centering
    \subfloat[Dask execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_dask-bag_baseline_gantt.png}%
    }

@@

\begin{figure}[p]
    \centering
    \subfloat[Histogram makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_instance.png}%
    }

@@

\begin{figure}[p]
    \centering
    \subfloat[Histogram makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_splits.png}%
    }

@@

%%%%% DISCUSSION %%%%%
\section{Discussion}
\subsection{Serialization}
We think that serialization could have an important effect on the makespan of the
application. This could potentially slow down the application when a lot of tasks are
scheduled.

>>>>

% Histogram
\subsection{Histogram}
For our second experiment we find the frequency of the voxels intensity in BigBrain
and save them as a tuple in a file. In this experiment the end results depends on all
of the input results (see \ref{fig:tg-histo}). This allow us to study the behaviour
of the framework when task are dependent. Also this application require data
shuffling thus inter worker communication. In this application we decided to omit the
dask futures api as it is less realistic for this use case.

@@

%%% INCREMENTATION %%%
%% Instances
\subsection{Experiment 1: Number of instances}
Figure \ref{fig:inc_node}(a) shows that the incease in performance is not
proportional to the number of worker which differ form what we would expect; it even
decrease when we reach 8 instances (64 workers). This is explained by an increase in
IO time corrolated to the number of workers (Figure \ref{fig:inc_node}(b)), as more
worker access the nfs simultaneously it increase the stress put on the system which
result in bottleneck, errors and slow down.

On the one hand, Dask seems better when
using a single worker. On the other hand, Spark makespan decrease faster for low
level of parallelism. However Dask quickly catch up at high level of parallelism.
This makes us think that the scheduler in Dask might be better

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_instances.png}%
    }

@@

%% Iterations
\subsection{Experiment 1: Number of iterations}
In Figure \ref{fig:inc_itr} we see that spark and the dask bag api are equivalent in
term of performance. The dask delayed api seems to perform well with low amount of
task but grow faster the spark and dask bag. We think this is because dask delayed
often schedule a block on different worker of the same instance which cause small
delay everytime due to inter worker communication. This is good when there is fewer
tasks as is make the io between block go out of sync hence lowering the io bottleneck
observed earlier however as the number of tasks increases those small delays become
significant. The dask futures api seems to outperform all the other apis but this is
most likely because the tasks are not inter dependent thus this application benifits
from the less optimal but faster scheduling brought by dask futures.

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_iterations.png}%
    }

@@

%% Sleep time
\subsection{Experiment 1: Sleep delay}
As Figure \ref{fig:inc_sleep}

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_sleeptime.png}%
    }

@@

\begin{figure}[htp]
    \centering
    \subfloat[Incrementation makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/Incrementation_splits.png}%
    }

@@

\begin{figure}[htp]
    \centering
    \subfloat[Dask execution timeline]{%
      \includegraphics[clip,width=\columnwidth]{images/inc_dask-bag_baseline_gantt.png}%
    }

@@

\begin{figure}[htp]
    \centering
    \subfloat[Histogram makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_instance.png}%
    }

@@

\begin{figure}[htp]
    \centering
    \subfloat[Histogram makespan]{%
      \includegraphics[clip,width=\columnwidth]{images/histo_splits.png}%
    }

@@

%%%%% DISCUSSION %%%%%
\section{Discussion}
\subsection{IO Time}

\subsection{Serialization}
We think that serialization could have an important effect on the makespan of the
application. This could potentially slow down the application when a lot of tasks are
scheduled.
